\emph{Gaia} DR2 adds clues for dynamical ejection of a $\sim$$150\,M_\odot$ star

### 2018-05-22 VFTS682.tex
minor in Sec. 2.2

\subsection{HST astrometry for VFTS682}
Recently, \citet{platais:18} presented HST  astrometry and proper
motions in the 30 Doradus region based on two epochs of
observations; the first epoch (GO-12499; P.I.: D.~J.~Lennon)
in October 3-8 2011 and the second epoch (GO-13359) in
October 6-11 2014, both using the F775W filter.
The second epoch was designed to match the pointing and
orientation of the first epoch as exactly as possible so
that the displacement measurements could be purely differential.
While most bright massive stars (V$<$14) were saturated in
their data and missing from that catalog, due to its
high extinction, E(B-V)=0.9, this star is faint enough
to be included in that catalog. Its proper motions are
listed in \Tabref{tab:vfts682}. For
large distances ($\gtrsim50$\,kpc), HST astrometry can compete or even
exceed \emph{Gaia} data in quality.

@@

Since these measures are completely independent from ours, we can take
an average weighted with $1/\delta \mu_i^2$ (cf.~notation in
\Eqref{eq:mean}), obtaining $\delta\mu_\mathrm{RA}=\pm\,\mathrm{mas\
  yr^{-1}}$ and $\delta\mu_\mathrm{DEC}=\pm\,\mathrm{mas\
  yr^{-1}}$.

@@

\todo{redo below with average HST+Gaia?Actually redo also calculation
  of $v_\mathrm{pec}$}

>>>>

\subsection{HST astrometry for VFTS682}
Recently, \citet{platais:18} presented HST  astrometry and proper
motions in the 30 Doradus region based on two epochs of
observations; the first epoch (GO-12499; P.I.: D.~J.~Lennon)
in October 3-8 2011 and the second epoch (GO-13359) in
October 6-11 2014, both using the F775W filter.
The second epoch was designed to match the pointing and
orientation of the first epoch as exactly as possible so
that the displacement measurements could be purely differential.
While most bright massive stars (V$<$14) were saturated in
their data and missing from that catalog, due to its
high extinction, this star is faint enough
to be included in that catalog. Its proper motions are
listed in \Tabref{tab:vfts682}. For
large distances ($\gtrsim50$\,kpc), HST astrometry can compete or even
exceed \emph{Gaia} DR2 data in quality.

@@

% Since these measures are completely independent from ours, we can take
% an average weighted with $1/\delta \mu_i^2$ (cf.~notation in
% \Eqref{eq:mean}), obtaining $\delta\mu_\mathrm{RA}=\pm\,\mathrm{mas\
%   yr^{-1}}$ and $\delta\mu_\mathrm{DEC}=\pm\,\mathrm{mas\
%   yr^{-1}}$.

@@

\todo{redo below with HST only and Gaia only?Redo also calculation
  of $v_\mathrm{pec}$}
